Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-27 proposal/prop.tex
typo

The interesting step for us is now to realize that the {\it parameter
  curves\/} shown in the figure do not need, or indeed, must not, be
themselves infinitely precise real numbers, but they must themselves
incorporate in some way a theory consistent with forbidding absolute
precision.  In practice, then, the sinusoidal lines in Figure
\ref{houghline.fig} all become fuzzy, and the accumulation of these
fuzzy distributions produces peaks of likelihood around the values
$(d_0, \theta_0)$ that are the optimal choices for the line describing
the set of data.  Note that even {\it one\/} data point provides
evidence on a set of hypotheses. The simple analysis we have outlined
here is easily extended to much more complex situations in higher
dimensions (see, e.g.,~\cite{BallardGenHough1981}).  Our point here is
that essentially any physical theory that would ordinarily be
described by a mathematical model using infinite precision numbers is
potentially nonsensical from a computational point of view: computer
scientists know perfectly well, and have been dealing with since the
time of Turing and Shannon, that every single bit of precision in any
number has a cost, and that there is not enough energy in the universe
to computer even one general real number.  Thus the combination of
physical models that, in some intrinsic fashion, contain only
computable numbers, with theories of measurement and evidence in the
fashion of the Hough transform example we have just presented, could
contain the outline of entirely new ways of understanding what
mathematical models of the physical world and its measurement actually
could be.

>>>>

The interesting step for us is now to realize that the {\it parameter
  curves\/} shown in the figure do not need, or indeed, must not, be
themselves infinitely precise real numbers, but they must themselves
incorporate in some way a theory consistent with forbidding absolute
precision.  In practice, then, the sinusoidal lines in Figure
\ref{houghline.fig} all become fuzzy, and the accumulation of these
fuzzy distributions produces peaks of likelihood around the values
$(d_0, \theta_0)$ that are the optimal choices for the line describing
the set of data.  Note that even {\it one\/} data point provides
evidence on a set of hypotheses. The simple analysis we have outlined
here is easily extended to much more complex situations in higher
dimensions (see, e.g.,~\cite{BallardGenHough1981}).  Our point here is
that essentially any physical theory that would ordinarily be
described by a mathematical model using infinite precision numbers is
potentially nonsensical from a computational point of view: computer
scientists know perfectly well, and have been dealing with since the
time of Turing and Shannon, that every single bit of precision in any
number has a cost, and that there is not enough energy in the universe
to compute even one general real number.  Thus the combination of
physical models that, in some intrinsic fashion, contain only
computable numbers, with theories of measurement and evidence in the
fashion of the Hough transform example we have just presented, could
contain the outline of entirely new ways of understanding what
mathematical models of the physical world and its measurement actually
could be.
